Fictitious Play in Network Aggregative Games

### 2021-04-23 Documents/FP in NAGs/FPNAG.tex
minor edits

	\newpage
	\section{Introduction}
		\subsection{Related Work}
		Main articles: Ewerhart (FP in Networks), Grammatico (Nash Equilibrium seeking in NA games), Perrin (FP in mean field games), Harris (FP in 2 player games).
		\subsection{Contributions}

		The main contribution of this work is to study the behaviour of the Fictitious Play Learning Algorithm, in continuous time, when applied on a Network Aggregative Matrix Game. We first show that a Nash Equilibrium exists and that Fictitious Play admits solutions in this setting. In particular, we study zero-sum games and show that Fictitious Play converges to a fixed point, which for a simple network corresponds to a Nash Equilibrium. In addition, we find that, for games which are not zero-sum, agents following Continuous Time Fictitious Play are able to achieve no regret.

@@

		\ah{Possible additions: 1) Show that the flow is unique almost everywhere in CTFP. 2) Show the same results (i.e. existence and convergence) for Discrete Time Fictitious Play.}
		\section{Preliminaries}
	\subsection{Network Aggregative Games}
	\label{sec::NAG}

	The model we consider is that there is a set $\agentset = {1, ... ,
	N}$ of agents who are connected through an underlying interaction graph. This graph is given by
	the tuple $(\agentset, (\edgeset, \weightset))$ in which $\edgeset$ is the set of all pairs $(\mu,
	\nu) \in \agentset \times \agentset$ such that agent $\mu$ and agent $\nu$ are connected. Then,
	the set of neighbours of agent $\mu$ is denoted as $N^\mu = \{\nu \in \agentset \, : \, (\mu,
	\nu) \in \edgeset\}$. $\weightset
	\in M_N(\mathbb{R})$ is the weighted adjacency matrix whose elements $w^{\mu \nu}$ expresses the
	importance that agent $\mu$ places on agent $\nu$. Note that if $(\mu, \nu) \not \in \edgeset$
	then $w^{\mu \nu} = 0$ and $\wmunu \in (0, 1]$ otherwise.

	As a network game, each agent $\mu$ has an associated set of pure strategies $\actionset{\mu}$
	which has cardinality $|\actionset{\mu}| = n$. Then we can construct the unit-simplex on this
	action set as $\Delta_\mu := \{x \in \mathbb{R}^n \, : \, \sum_i \xmuaction{i} = 1\}$ where
	$\xmuaction{i}$ is the probability with which agent $\mu$ plays the pure strategy $i$. As such
	we refer to $\xmu$ as the \emph{state} of agent $\mu$ (this is often referred to as $\mu$'s
	mixed strategy). Also associated with each agent is a utility function $u^\mu(\xmu, \xnotmu)$ in
	which we use the standard notation $-\mu$ to refer to all agents other than $\mu$. Notice that
	this requires that each agent plays the same strategy against all of their neighbours.

	With all of the above definitions, we can formalise the network aggregative (NA) game as the tuple
	$\Gamma = (\agentset, (\edgeset, \weightset), (\actionset{\mu}, \utility{\mu})_{\mu \in \mathcal{N}})$.

	What is unique about the NA game is the structure of the payoffs themselves. In this format,
	each agent is receives a reference $\sigma$ which is a weighted sum of each of their
	neighbours state. Formally

	\begin{equation}
		\sigma^\mu = \sum_{\nu \in N^\mu} \wmunu \xnu.
	\end{equation}

	Then, the agent's must optimise their payoff with respect to this reference vector. Thus,
	instead of having to consider the actions of the entire population, or play individual games
	against each of their neighbours, the agent only has to consider $\sigma^\mu$ as a `measurement'
	of the local aggregate state and optimise with respect to this measurement. This allows us to
	make the reduction $u^\mu(\xmu, \xnotmu) = u^\mu(\xmu, \refmu)$. In particular, we consider that
	the agent is engaged in a matrix game against the reference vector so that

	\begin{equation}
		u^\mu(\xmu, \refmu) = \xmu \cdot A^\mu \refmu = \xmu \cdot A^\mu \weightedsum.
	\end{equation}

	where $A^\mu$ is the payoff matrix associated to agent $\mu$. Note that this means we could have
	written the game $\Gamma$ with the payoff matrices $A^mu$ in place of the utility functions
	$\utility{\mu}$. The NA game allows for the reduction of a
	multiplayer game into a series of two-player games. The agent's goal is to maximise their payoff
	with respect to the reference vector. As such, we define the best response correspondence
	$BR^\mu$ which maps any $\refmu$ the set $\arg \max_{y \in \Delta_\mu} {u^\mu(y, \refmu)}$. This
	leads naturally to the definition of a Nash Equilibrium in an NA Game as

	\begin{definition}(NE)
		The set of vectors $\{ \NE{\mu}\}_{\mu \in \agentset}$ is an NE if, for all $\mu$,

		\begin{equation*}
		\NE{\mu} \in \arg \max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\mu \backslash \{\bar{\mu}\}} \wmunu \NE{\nu}).
		\end{equation*}

	\end{definition}

@@

	\ah{For Francesco: is it worth giving a quick introduction to Fictitious Play by talking about two player games?}

	Fictitious Play requires that, at the current time, each agent considers the average behaviour
	of their opponent in the past and play a best response to that strategy. This is best
	illustrated in the two-player setting. Consider the two player normal form game $\Gamma_2 = (\{
	1, 2\}, ((S^1, A), (S^2, B)))$ so that $A$ and $B$ are the payoff matrices of agent $1$ and $2$
	respectively. As a remark, note that we can write the two player normal form game as an NA game
	simply by requiring that $\edgeset = \{(1, 2), (2, 1)\}$ and $\weightset$ is a 2x2 matrix with
	zeros on its leading diagonal and ones on the off diagonal. We write the time-average of both
	agents' strategies as

	\begin{align}
		\alpha^1 = \frac{1}{t} \int_0^T x^1(t) \, dt \\
		\alpha^2 = \frac{1}{t} \int_0^T x^2(t) \, dt \\
	\end{align}

@@

	We extend this naturally to the NA game $\Gamma$ by requiring that each agent update their
	strategy according to the time average of their reference vector $\refmu$. To formalise this, we
	write

	\begin{equation}
		\avgref{\mu} = \frac{1}{t} \int_0^t \refmu(s) \; ds.
	\end{equation}

	Using this, we follow in the footsteps of Ewerhart \cite{} and Harris \cite{} to define
	Fictitious Play in continuous time.

	\begin{definition}[Continuous Time Fictitious Play (CTFP)]
		A CTFP is defined as a measurable map $m$ with components $m_i$ such that for all $i$ and all $t \geq 1$, $m_i: [0, \infty) \rightarrow \Delta_i$ satisfies $m_i(t) \in BR_i(\alpha_{\sigma_i})$ for all $t \geq 1$.

		We can think of this definition as saying that the player plays some arbitrary strategy before $t = 1$, but beyond this it must play a best response to the time average of its reference signal.
	\end{definition}

@@

>>>>

	\newpage
	\section{Introduction}
		\subsection{Contributions}

		The main contribution of this work is to study the
                behaviour of the Fictitious Play Learning Algorithm,
                in continuous time, when applied on a Network
                Aggregative Matrix Game.
\fb{why FP and NAG are important?}

                We first show that a Nash
                Equilibrium exists and that Fictitious Play admits
                solutions in this setting. In particular, we study
                zero-sum games and show that Fictitious Play converges
                to a fixed point, which for a simple \fb{define simple} network
                corresponds to a Nash Equilibrium. In addition, we
                find that, for games which are not zero-sum, agents
                following Continuous Time Fictitious Play are able to
                achieve no regret.

@@

		\ah{Possible additions: 1) Show that the flow is
                  unique almost everywhere in CTFP. 2) Show the same
                  results (i.e. existence and convergence) for
                  Discrete Time Fictitious Play.}

		\subsection{Related Work}
		Main articles: Ewerhart (FP in Networks), Grammatico
                (Nash Equilibrium seeking in NA games), Perrin (FP in
                mean field games), Harris (FP in 2 player games).

		\section{Preliminaries}
	\subsection{Network Aggregative Games}
	\label{sec::NAG}

	The model we consider is that there is a set $\agentset = {1,
         \ldots , N}$ of agents who are connected through an underlying
        interaction graph. This graph is given by the tuple
        $(\agentset, (\edgeset, \weightset))$ in which $\edgeset$ is
        the set of all pairs $(\mu, \nu) \in \agentset \times
        \agentset$ such that agent $\mu$ and agent $\nu$ are
        connected.
        \fb{
          \begin{definition}[Interaction Graph]
  Given a set $\agentset$ of agents, an {\em interaction graph} $I = (\agentset, (\edgeset, \weightset))$ such that
  \begin{itemize}
  \item $\edgeset \subseteq \agentset \times \agentset$.        Then, the set of neighbours of agent $\mu$ is
        denoted as $N^\mu = \{\nu \in \agentset \, : \, (\mu, \nu) \in
        \edgeset\}$.
    \item $\weightset \in M_N(\mathbb{R})$ is the weighted
        adjacency matrix whose elements $w^{\mu \nu}$ expresses the
        importance that agent $\mu$ places on agent $\nu$. If $(\mu, \nu) \not \in \edgeset$ then $w^{\mu \nu} = 0$;        $\wmunu \in (0, 1]$ otherwise.
  \end{itemize}
\end{definition}
}

	As a network game, each agent $\mu$ has an associated set of
        pure strategies $\actionset{\mu}$ which has cardinality
        $|\actionset{\mu}| = n$. \fb{what is a strategy then? how can
          we define them if we didn't introduce actions?}

        Then we can construct the \fb{unit-simplex ?} on this action
        set as $\Delta_\mu := \{x \in \mathbb{R}^n \, : \, \sum_i
        \xmuaction{i} = 1\}$ where $\xmuaction{i}$ is the probability
        with which agent $\mu$ plays the pure strategy $i$. As such we
        refer to $\xmu$ as the \emph{state} of agent $\mu$ (this is
        often referred to as $\mu$'s mixed strategy). Also associated
        with each agent is a utility function $u^\mu(\xmu, \xnotmu)$
        in which we use the standard notation $-\mu$ to refer to all
        agents other than $\mu$. Notice that this requires that each
        agent plays the same strategy against all of their neighbours.

	With all of the above definitions, we can formalise the
        network aggregative (NA) game as the tuple $\Gamma =
        (\agentset, (\edgeset, \weightset), (\actionset{\mu},
        \utility{\mu})_{\mu \in \mathcal{N}})$. \fb{preferably use a
          definition environment.}

	What is unique about the NA game is the structure of the
        payoffs themselves. In this format, each agent is receives a
        reference $\sigma$ which is a weighted sum of each of their
        neighbours state. Formally
%
	\begin{equation}
		\sigma^\mu = \sum_{\nu \in N^\mu} \wmunu \xnu.
	\end{equation}

	Then, the agent's must optimise their payoff with respect to
        this reference vector. Thus, instead of having to consider the
        actions of the entire population, or play individual games
        against each of their neighbours, the agent only has to
        consider $\sigma^\mu$ as a `measurement' of the local
        aggregate state and optimise with respect to this
        measurement. This allows us to make the reduction $u^\mu(\xmu,
        \xnotmu) = u^\mu(\xmu, \refmu)$. In particular, we consider
        that the agent is engaged in a matrix game against the
        reference vector so that
%
	\begin{equation}
		u^\mu(\xmu, \refmu) = \xmu \cdot A^\mu \refmu = \xmu
                \cdot A^\mu \weightedsum.
	\end{equation}
	where $A^\mu$ is the payoff matrix associated to agent
        $\mu$. Note that this means we can write the game
        $\Gamma$ with the payoff matrices $A^mu$ in place of the
        utility functions $\utility{\mu}$. The NA game allows for the
        reduction of a multiplayer game into a series of two-player
        games. The agent's goal is to maximise their payoff with
        respect to the reference vector. As such, we define the best
        response correspondence $BR^\mu$ which maps any $\refmu$ the
        set $\arg \max_{y \in \Delta_\mu} {u^\mu(y, \refmu)}$. This
        leads naturally to the definition of a Nash Equilibrium in an
        NA Game as

	\begin{definition}(NE)
		The set of vectors $\{ \NE{\mu}\}_{\mu \in \agentset}$ is an NE if, for all $\mu$,	
		\begin{equation*}
		\NE{\mu} \in \arg \max_{x \in \Delta_\mu} u^\mu(x, w^{\mu \mu} x + \sum_{\nu \in N^\mu \backslash \{\bar{\mu}\}} \wmunu \NE{\nu}).
		\end{equation*}	
	\end{definition}
        \fb{It this a definition or rather a lemma?}

@@

	\ah{For Francesco: is it worth giving a quick introduction to Fictitious Play by talking about two player games?}
\fb{I'd rather give the definition first and then the example.}

	Fictitious Play requires that, at the current time, each agent
        considers the average behaviour of their opponent in the past
        and play a best response to that strategy. This is best
        illustrated in the two-player setting. Consider the two player
        normal form game $\Gamma_2 = (\{ 1, 2\}, ((S^1, A), (S^2,
        B)))$ so that $A$ and $B$ are the payoff matrices of agent $1$
        and $2$ respectively. As a remark, note that we can write the
        two player normal form game as an NA game simply by requiring
        that $\edgeset = \{(1, 2), (2, 1)\}$ and $\weightset$ is a 2x2
        matrix with zeros on its leading diagonal and ones on the off
        diagonal. We write the time-average of both agents' strategies
        as
%
	\begin{align}
		\alpha^i = \frac{1}{t} \int_0^T x^i(t) \, dt & \text{ for $i \in \{1, 2\}$}
%		\alpha^2 = \frac{1}{t} \int_0^T x^2(t) \, dt \\
	\end{align}
        \fb{why using an integral rather than a simple summation?}

        \fb{decide whether you start enumerations from 1 or 0.}

@@

	We extend this naturally to the NA game $\Gamma$ by requiring that each agent update their
	strategy according to the time average of their reference vector $\refmu$. To formalise this, we
	write
	\begin{equation}
		\avgref{\mu} = \frac{1}{t} \int_0^t \refmu(s) \; ds.
	\end{equation}

	Using this, we follow in the footsteps of Ewerhart \cite{} and Harris \cite{} to define
	Fictitious Play in continuous time.
%
	\begin{definition}[Continuous Time Fictitious Play (CTFP)]
		A CTFP is defined as a measurable map $m$ with components $m_i$ such that for all $i$ and all $t \geq 1$, $m_i: [0, \infty) \rightarrow \Delta_i$ satisfies $m_i(t) \in BR_i(\alpha_{\sigma_i})$ for all $t \geq 1$.
	\end{definition}

		We can think of this definition as saying that the player plays some arbitrary strategy before $t = 1$, but beyond this it must play a best response to the time average of its reference signal.

@@

\fb{discuss how restrictive each of these assumptions is.}
